Estudio variabilidad estructural proteica

### 2016-05-09 AllFamilys.Rmd
cambios 09/05/2016

# Create vectors to keep data.
v.theo.MSDi.s.n = c()
v.exp.MSDi.s.n = c()

@@

@@

  m.exp.smooth.norm.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.exp.smooth.norm.dr.squarei.csv", sep = "")))

 exp.MSDi.s.n = colMeans(m.exp.smooth.norm.dr.squarei, na.rm = T )

  # Read theoretical data#
  m.theo.smooth.norm.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.smooth.norm.dr.squarei.csv", sep = "")))

 theo.MSDi.s.n = colMeans(m.theo.smooth.norm.dr.squarei, na.rm = T)

  ## Fit theoretical data with experimental data.

  fit.s.n = lm(exp.MSDi.s.n ~ theo.MSDi.s.n)
  fit.MSDi.s.n = fitted.values(fit.s.n)

  # Concatenate information.
  v.theo.MSDi.s.n = c(v.theo.MSDi.s.n, fit.MSDi.s.n)

  exp.MSDi.s.n = exp.MSDi.s.n[!is.na(exp.MSDi.s.n)]
  v.exp.MSDi.s.n = c(v.exp.MSDi.s.n, exp.MSDi.s.n)
}

# Caluclate measures.
R2.s.n = cor(theo.MSDi.s.n, exp.MSDi.s.n) ^ 2  
MSE.s.n = mean((theo.MSDi.s.n - exp.MSDi.s.n) ^ 2)

```

All families fitted smooth and normalized MSD profiles

```{r}
plot(theo.MSDi.s.n, type = "l", xlab = "site", ylab = "Theoretical")
```

```{r}
plot(exp.MSDi.s.n, type = "l", col = "red", xlab = "site",  ylab = "Experimental")
```

```{r}
plot(theo.MSDi.s.n, type = "l", xlab = "site", ylab = "Merge")
points(exp.MSDi.s.n, col = "red", type = "l")
legend("topleft", paste("R^2", round(R2.s.n, digits = 2), " ", "MSE", signif(MSE.s.n, digits = 4)), bty = "n", text.col = "red")
```

>>>>

# Create vectors to keep data.
v.v.theo.MSDi = c()
v.v.exp.MSDi = c()
v.R2 = c()
v.MSE = c()

@@

# Create a list of selection regimens.
all.betas <- list("strong.sel", "medium.sel", "weak.sel", "no.sel")

# Start a loop for each beta.
for (beta in (all.betas)) {

  # Create vectors to keep data.
  v.theo.MSDi = c()
  v.exp.MSDi = c()

@@

    m.exp.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.exp.smooth.norm.dr.squarei.csv", sep = "")))
    exp.MSDi = colMeans(m.exp.dr.squarei, na.rm = T)

    # Read theoretical data#
    m.theo.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.smooth.norm.dr.squarei.csv", sep = "")))
    theo.MSDi = colMeans(m.theo.dr.squarei, na.rm = T)

    # Fit theoretical data with experimental data.
    fit = lm(exp.MSDi ~ theo.MSDi)
    fit.MSDi = fitted.values(fit)

    # Save and concatenale information.
    v.theo.MSDi = c(v.theo.MSDi, fit.MSDi)
    exp.MSDi = exp.MSDi[!is.na(exp.MSDi)]
    v.exp.MSDi = c(v.exp.MSDi, exp.MSDi)

  }

  # Caluclate measures.
  R2 = cor(v.theo.MSDi, v.exp.MSDi) ^ 2  
  MSE = mean((v.theo.MSDi - v.exp.MSDi) ^ 2)

  v.v.theo.MSDi = c(v.v.theo.MSDi, v.theo.MSDi)
  v.v.exp.MSDi = c(v.v.exp.MSDi, v.exp.MSDi)

  v.R2 = c(v.R2, R2)
  v.MSE = c(v.MSE, MSE)
}

n.sites.all.families = length(v.v.theo.MSDi)/4
```

All families fitted smoothed and normalized MSD profiles with different selection regimens:

```{r}
plot(v.v.theo.MSDi[1:n.sites.all.families], type = "l", main = " Strong selection", xlab = "site", ylab = "Merge")
points(v.v.exp.MSDi[1:n.sites.all.families], col = "red", type = "l")
legend("topleft", paste("R ^ 2", round(v.R2[1], digits = 3), "MSE", signif(v.MSE[1], digits = 4)), bty = "n", text.col = "red")
```

```{r}
plot(v.v.theo.MSDi[(n.sites.all.families + 1):(2 * n.sites.all.families)], type = "l", main = " Medium selection", xlab = "site", ylab = "Merge")
points(v.v.exp.MSDi[(n.sites.all.families + 1):(2 * n.sites.all.families)], col = "red", type = "l")
legend("topleft", paste("R^2", round(v.R2[2], digits = 3), "MSE", signif(v.MSE[2], digits = 4)), bty = "n", text.col = "red")
```

```{r}
plot(v.v.theo.MSDi[((2 * n.sites.all.families) + 1):(3 * n.sites.all.families)], type = "l", main = " Weak selection", xlab = "site", ylab = "Merge")
points(v.v.exp.MSDi[((2 * n.sites.all.families) + 1):(3 * n.sites.all.families)], col = "red", type = "l")
legend("topleft", paste("R^2", round(v.R2[3], digits = 3), "MSE", signif(v.MSE[3], digits = 4)), bty = "n", text.col = "red")
```

```{r}
plot(v.v.theo.MSDi[((3 * n.sites.all.families) + 1):(4 * n.sites.all.families)], type = "l", main = " No selection", xlab = "site", ylab = "Merge")
points(v.v.exp.MSDi[((3 * n.sites.all.families) + 1):(4 * n.sites.all.families)], col = "red", type = "l")
legend("topleft", paste("R^2", round(v.R2[4], digits = 3), "MSE", signif(v.MSE[4], digits = 4)), bty = "n", text.col = "red")
```

*Black:* Theoretical mean.

*Red:* Experimental mean.

### 2016-05-09 MultipleReportAllBetas.Rmd
cambios 09/05/2016

# Source functions.
source("FUNCTIONS/CalculateGroupsMeansQuantiles.R")

@@

# Read betas.
betas.fname.id <- paste(family, "_", p.ref, "_R0_", R0, sep = "")
all.betas <- read.csv(file.path(out.dir, paste(betas.fname.id, "_out_all.betas.csv", sep = "")))

@@

Los perfiles teoricos suavizados y normalizados de MSDi fueron fiteados con los perfiles exterimentales. Se compararon y se calcularon R^2 y MSE. Se indica el regimen de selección usada.

>>>>

```{r}
# Source functions.
source("FUNCTIONS/CalculateGroupsMeansQuantiles.R")

@@

# Read betas.
all.betas <- list("strong.sel", "medium.sel", "weak.sel", "no.sel")

@@

Los perfiles teoricos suavizados y normalizados de MSDi fueron fiteados con los perfiles exterimentales. Se compararon y se calcularon R^2 y MSE. Se indica el regimen de selecci?n usada.
